---
title: "EDA for KMA Seoul 2011~2020"
output:
  html_document:
    df_print: paged
---

```{r, include = FALSE}
source("../get_kma_data.R")
kma1520 <- get_partial_KMA(2015, 2020)

kma1520[is.na(kma1520[9]),][9] <- 0
dates <- unlist(kma1520[3], use.names = FALSE)
kma15 <- kma1520[unlist(lapply(dates, function(x) { startsWith(x, "2015") })),]
daily_idcs <- as.integer(rownames(kma15))
```

### Data structure sample by head

```{r, echo = FALSE}
head(kma1520)
```

### Plot of 2015 daily min/max temperature time

```{r, echo = FALSE}
plot(daily_idcs, unlist(kma15[6]), main = "2015년 일 최저기온시각", xlab = "",
     ylab = "최저기온시각(hhmi)")
plot(daily_idcs, unlist(kma15[8]), main = "2015년 일 최고기온시각", xlab = "",
     ylab = "최고기온시각(hhmi)")
```

### Plot of 2015 daily min/avg/max temperature

```{r, echo = FALSE}
plot(daily_idcs, unlist(kma15[4]), main = "2015년 일 최저/평균/최고 기온", xlab = "",
     ylab = "기온", xlim = c(1,365), ylim = c(-20.0, 40.0))
par(new = TRUE)
plot(daily_idcs, unlist(kma15[5]), main = "", xlab = "", ylab = "",
     xlim = c(1, 365), ylim = c(-20.0, 40.0), axes = FALSE, col = "blue")
par(new = TRUE)
plot(daily_idcs, unlist(kma15[7]), main = "", xlab = "", ylab = "",
     xlim = c(1, 365), ylim = c(-20.0, 40.0), axes = FALSE, col = "red")
par(new = FALSE)
```

### Correlation between 2015 daily min/avg/max temperature

```{r, echo = FALSE}
maxtemp <- kma15[7]
avgtemp <- kma15[4]
mintemp <- kma15[5]
cor_max_min <- cor(maxtemp, mintemp)
cor_max_avg <- cor(maxtemp, avgtemp)
cor_avg_min <- cor(avgtemp, mintemp)
sprintf("cor(maxTemp, minTemp): %f", cor_max_min)
sprintf("cor(maxTemp, avgTemp): %f", cor_max_avg)
sprintf("cor(avgTemp, minTemp): %f", cor_avg_min)
```

### (Timeseries) Multiple Regression with 2015 daily max/min temperature

```{r, echo = FALSE}
tsmaxtemp <- ts(maxtemp, start = 1, frequency = 1)
tsmintemp <- ts(mintemp, start = 1, frequency = 1)
tsmaxmintemp <- ts.union(tsmaxtemp, tsmintemp)
print("Head of tsmaxmintemp")
head(tsmaxmintemp)
plot(tsmaxmintemp, main = "Max/Min Temp TS", xlab = "", col = "mediumpurple3")
maxmintemp_lm <- lm(tsmaxtemp ~ tsmintemp, data = tsmaxmintemp)
summary(maxmintemp_lm)
pred_maxtemp <- predict(maxmintemp_lm)
residuals <- unlist(maxtemp) - pred_maxtemp
plot(tsmaxtemp, col = "red", ylim = c(-20, 40), ylab = "", xlab = "",
     main = "max temp obs.(red) vs prediction(blue)")
lines(ts(pred_maxtemp, start = c(1, 1), frequency = 1), col = "blue")
plot(daily_idcs, residuals,
     main = "Test of the regression model validity by residuals")
abline(lm(residuals ~ daily_idcs))
```

### Durbin-Watson test & autocorrelation correction by lagging 1 step

``` {r, echo = FALSE}
library(carData)
library(car)
dwTestRes <- durbinWatsonTest(maxmintemp_lm)
if (dwTestRes[["p"]] < 0.05) {
  print("The timeseries data has autocorrelation so we need to fix it!!!")
  tsmaxmintempC <- ts.union(tsmaxtemp, tsmintemp,
                            tsmaxtemp1 = lag(tsmaxtemp, -1))
  maxmintemp_lmC <- lm(tsmaxtemp ~ tsmintemp + tsmaxtemp1,
                       data = tsmaxmintempC)
  print(summary(maxmintemp_lmC))
  pred_maxtempC <- predict(maxmintemp_lmC)
  residualsC <- unlist(maxtemp)[2:length(unlist(maxtemp))] - pred_maxtempC
  plot(tsmaxtemp[2:length(tsmaxtemp)],
       col = "red", ylim = c(-20, 40), ylab = "", xlab = "",
       main = "max temp obs.(red) vs corrected prediction(blue)")
  lines(ts(pred_maxtempC, start = c(1, 1), frequency = 1), col = "blue")
  plot(daily_idcs[1:length(daily_idcs) - 1], residualsC,
       main = "Test of the corrected regression model validity by residuals")
  abline(lm(residualsC ~ daily_idcs[1:length(daily_idcs) - 1]))
}
```

### Cochrane-Orcutt method for autocorrelation correction

``` {r, echo = FALSE}
library(zoo)
library(lmtest)
library(orcutt)
if (dwTestRes[["p"]] < 0.05) {
  print("Let's correct autocorrelation with the Cochrane-Orcutt method")
  maxmintemp_lmO <- cochrane.orcutt(maxmintemp_lm)
  print(summary(maxmintemp_lmO))
}
```

### Generalized Time Series Regression

``` {r, echo = FALSE}
library(forecast)
if (dwTestRes[["p"]] < 0.05) {
  fit <- auto.arima(tsmaxtemp, xreg = tsmintemp)
  Box.test(residuals(fit), type = "Ljung", lag = 1)
  fake_mintemps <- data.frame(rep(mean(tsmintemp[361:365]), 4))
  colnames(fake_mintemps) <- colnames(kma15[5])
  fake_mintempsTS <- ts(fake_mintemps, start = 1, frequency = 1)
  fcast <- forecast(fit, xreg = fake_mintempsTS, h = 4)
  plot(fcast, main = "Generalized time series regression model prediction")
}
```

### Box plot of 2015 daily min/avg/max temperature

```{r, echo = FALSE}
boxplot(kma15[, c(5, 4, 7)])
#boxplot(kma20[, c(5, 4, 7)], add = TRUE, border = "red")
```

### Plot of 2015 daily precipitation

```{r, echo = FALSE}
plot(daily_idcs, unlist(kma15[9]), main = "2015년 일 강수량", xlab = "",
     ylab = "강수량")
```

### Plot of 2015 daily avg temperature & precipitation

```{r, echo = FALSE}
plot(unlist(kma15[4]), unlist(kma15[9]), main = "2015년 강수량/평균 기온 산점도",
     xlab = "평균기온", ylab = "강수량")
```
